---
title: "forestControl"
author: "Tom Wilson"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Installation

To install using `devtools`;

```R
devtools::install_github("wilsontom/forestControl")
```
or from source;

```sh
git clone https://github.com/wilsontom/forestControl
R CMD build forestControl
R CMD INSTALL forestControl_0.1.0.tar.gz
```
##

### Usage


All the necessary parameters that are required for calculating selection frequency false positive rates are extracted using the `extract_params` function. `extract_params` is compatible with both `randomForest` and `ranger` objects.

```{r, param_extract, random_forest}
library(forestControl)

# For randomForest models

randomForest_model <- randomForest::randomForest(
                                        iris[,-5],factor(iris$Species),
                                          ntree = 100, keep.forest = TRUE)


randomForest_parmas <- extract_params(randomForest_model)

randomForest_parmas
```

```{r, param_extract, ranger}
library(forestControl)

# For randomForest models

ranger_model <- ranger::ranger(factor(iris$Species) ~., iris[,-5],
                                  write.forest = TRUE, num.trees = 100)

ranger_params <- extract_params(ranger_model)

ranger_params
```
##

The output of `extract_params` is a list of four elements. 

  - __`Fn`__ is the total number of features which can be potentially used for splitting at each internal node. This parameter is refered to as `mrty` in the random forest package.
  
  - __`Ft`__ is the total number of features present in the data set
  
  - __`K`__ is the average number of binary tests (internal nodes) across the entire forest. 
  
  - __`Tr`__ is the total number of trees in the forest
  









